---
title: Attitudes Regarding the Assignment Process Among Navy Medical Corps Officers
date: "Date: `r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    toc: 4
    toc_float: true
    number_sections: true
---

This report covers the survey about attitudes collected by Richard Childers, MD and Joel Schofer, MD.

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set-options, echo=F}
# cat("Working directory: ", getwd())
report_render_start_time <- Sys.time()
opts_chunk$set(
  results      = 'show', 
  comment      = NA, 
  tidy         = FALSE,
  # dpi        = 400,
  # out.width  = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 7, 
  fig.height   = 4, 
  fig.path     = 'figure-png/'
)

echo_chunks    <- FALSE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) #So the output is 25% wider than the default.
read_chunk("./analysis/survey-response-1/survey-response-1.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load 'sourced' R files.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echo_chunks, message=message_chunks}
```

<!-- Load packages, or at least verify they're available on the local machine.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echo_chunks, message=message_chunks}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echo_chunks, results='show', message=message_chunks}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r rmd-specific, echo=echo_chunks, message=message_chunks}
# Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
#   It should be rare (and used cautiously), but sometimes it makes sense to include code in Rmd 
#   that doesn't live in the codebehind R file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echo_chunks, results='show', message=message_chunks}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echo_chunks, results='show', message=message_chunks}
```

Summary {.tabset .tabset-fade .tabset-pills}
============================================

Notes 
-----------------------------------

1. The current report covers `r nrow(ds)` responses.
1. We excluded `r sum(ds_everyone$year_executed_order < include_year_first, na.rm=T)` cases because their orders preceded the year `r include_year_first` and `r sum(is.na(ds_everyone$year_executed_order))` cases because the `year_executed_order` value was missing.

Unanswered Questions
-----------------------------------

Answered Questions
-----------------------------------

Graphs
============================================

Marginals


-----------------------------------

```{r marginals, echo=echo_chunks, message=message_chunks}
```

Scatterplots
-----------------------------------

```{r scatterplots, echo=echo_chunks, message=message_chunks, fig.width=7}
```

Relationships between Outcomes
============================================

```{r outcome-correlations, echo=echo_chunks, message=message_chunks}
```


Analyses - 1 Predictor
============================================

By Rank
-----------------------------------

```{r by-rank, echo=echo_chunks, message=message_chunks}
```

By Specialty Type
-----------------------------------

```{r by-specialty-type, echo=echo_chunks, message=message_chunks}
```

By Bonus Pay
-----------------------------------

```{r by-bonus-pay, echo=echo_chunks, message=message_chunks}
```

By Assignment Current Choice
-----------------------------------

```{r by-assignment-current-choice, echo=echo_chunks, message=message_chunks}
```


By Year
-----------------------------------

```{r by-year, echo=echo_chunks, message=message_chunks}
```


By Survey Lag
-----------------------------------

```{r by-survey_lag, echo=echo_chunks, message=message_chunks}
```


By Manning Proportion
-----------------------------------

```{r by-manning_proportion, echo=echo_chunks, message=message_chunks}
```


By Crtical War
-----------------------------------

```{r by-critical_war, echo=echo_chunks, message=message_chunks}
```

By Billet Current
-----------------------------------

```{r by-billet_current, echo=echo_chunks, message=message_chunks}
```


Analyses - 2 Predictors
============================================


By Rank and Specialty Type
-----------------------------------

```{r by-rank-and-specialty-type, echo=echo_chunks, message=message_chunks}
```

By Rank and Assignment Current Choice
-----------------------------------

```{r by-rank-and-assignment-current-choice, echo=echo_chunks, message=message_chunks}
```

By Rank and Bonus Pay
-----------------------------------

```{r by-rank-and-bonus_pay, echo=echo_chunks, message=message_chunks}
```


By Billet Current and Critical War
-----------------------------------

```{r by-billet_current-and-critical_war, echo=echo_chunks, message=message_chunks}
```


Session Information
============================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
} 
```
</details>

```{r session-duration, echo=FALSE}
report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.
