---
title: Attitudes Regarding the Assignment Process Among Navy Medical Corps Officers
date: "Date: `r Sys.Date()`"
output:
  html_document:
    keep_md: yes
    toc: 4
    toc_float: true
    number_sections: true
---

This report covers the survey about attitudes collected by Richard Childers, MD and Joel Schofer, MD.


Overall satisfaction was treated as a continuous response variable in a multiple regression.  The best fitting model included the three predictor variables of (a) specialty type, (b) officer rank, and (c) billet category, and no interaction terms.  Additional variables such as (d) bonus pay, (e) deployment rate, and (f) staffing status did not improve the model fit significantly, and therefore were removed.

Among the five levels in billet category, CONUS MTF had the highest values of satisfaction, and served as the reference group.  The CONUS Operational, OCONUS MTF, and Non-operational/non-clinical types were roughly .4 units less satisfied than CONUS MTF (after holding the other two predictors constant).  Similarly, physicians currently assigned to OCONUS operational were 1.1 units less satisfied than CONUS MTF.

Among the five levels in specialty type, the non-surgical physicians were most satisfied, and served as the reference group.  Residents were .2 units less satisfied, which was not significantly different.  However, the difference was significant between the nonsurgical type and the surgical (.3 units), family practice (.4 units) and operational (.7 units) types.

Officer rank was a continuous variable and had a significant positive slope: satisfaction increased with seniority.  Note that this does not necessarily mean an officer is expected to grow more satisfied as seniority increases; an alternate explanation is that less-satisfied officers leave the Navy while the more-satisfied officer remain and are promoted.  Longitudinal studies are needed to evaluate these competing explanations.

We were comfortable treating the 5-point Likert outcome as a continuous variable in the linear regression, after inspecting the graphs of frequencies and model diagnostics.  Thus we are making the assumption that the perceived distance between values 1 and 2 are roughly equivalent to the distance between values 4 and 5.  We performed ordered logistic regression that treats the outcome as an ordinal variable, which supported similar conclusions about the roles of the three predictors.  We chose to report the conventional regression for ease of interpretability.


<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set-options, echo=F}
# cat("Working directory: ", getwd())
report_render_start_time <- Sys.time()
opts_chunk$set(
  results      = 'show', 
  comment      = NA, 
  tidy         = FALSE,
  # dpi        = 1200,
  # out.width  = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 7, 
  fig.height   = 4, 
  fig.path     = 'figure-png/'
)

echo_chunks    <- FALSE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
options(width=100) #So the output is 25% wider than the default.
read_chunk("./analysis/survey-response-2/survey-response-2.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load 'sourced' R files.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echo_chunks, message=message_chunks}
```

<!-- Load packages, or at least verify they're available on the local machine.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echo_chunks, message=message_chunks}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echo_chunks, results='show', message=message_chunks}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r rmd-specific, echo=echo_chunks, message=message_chunks}
# Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
#   It should be rare (and used cautiously), but sometimes it makes sense to include code in Rmd 
#   that doesn't live in the codebehind R file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echo_chunks, results='show', message=message_chunks}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echo_chunks, results='show', message=message_chunks}
```

Summary {.tabset .tabset-fade .tabset-pills}
============================================

Notes 
-----------------------------------

1. The current report covers `r nrow(ds)` responses.
1. We excluded `r sum(ds_everyone$year_executed_order < include_year_first, na.rm=T)` cases because their orders preceded the year `r include_year_first` and `r sum(is.na(ds_everyone$year_executed_order))` cases because the `year_executed_order` value was missing.

Unanswered Questions
-----------------------------------

Answered Questions
-----------------------------------

Histograms
============================================

Univariate
-----------------------------------
```{r marginals, echo=echo_chunks, message=message_chunks}
```

Survey Response
============================================
```{r survey-response, echo=echo_chunks, message=message_chunks}
```

Relationships between Outcomes
============================================
```{r outcome-correlations, echo=echo_chunks, message=message_chunks}
```


Analyses - 1 Predictor
============================================

By Rank
-----------------------------------
```{r by-rank, echo=echo_chunks, message=message_chunks, results="asis"}
```

By Specialty Type
-----------------------------------
```{r by-specialty-type, echo=echo_chunks, message=message_chunks, results="asis"}
```

By Bonus Pay
-----------------------------------
```{r by-bonus-pay, echo=echo_chunks, message=message_chunks, results="asis"}
```

By Assignment Current Choice
-----------------------------------
```{r by-assignment-current-choice, echo=echo_chunks, message=message_chunks, results="asis"}
```


By Manning Proportion
-----------------------------------
```{r by-manning_proportion, echo=echo_chunks, message=message_chunks, results="asis"}
```

By Critical War
-----------------------------------
```{r by-critical_war, echo=echo_chunks, message=message_chunks, results="asis"}
```

By Billet Current
-----------------------------------
```{r by-billet_current, echo=echo_chunks, message=message_chunks, results="asis"}
```


Analyses - 2 Predictors
============================================


By Rank and Specialty Type
-----------------------------------
```{r by-rank-and-specialty-type, echo=echo_chunks, message=message_chunks, results="asis"}
```

By Rank and Assignment Current Choice
-----------------------------------
```{r by-rank-and-assignment-current-choice, echo=echo_chunks, message=message_chunks, results="asis"}
```

By Rank and Bonus Pay
-----------------------------------
```{r by-rank-and-bonus_pay, echo=echo_chunks, message=message_chunks, results="asis"}
```

By Billet Current and Critical War
-----------------------------------
```{r by-billet_current-and-critical_war, echo=echo_chunks, message=message_chunks, results="asis"}
```

By Bonus_pay and Manning_proportion
-----------------------------------
```{r by-bonus_pay-and-manning_proportion, echo=echo_chunks, message=message_chunks, results="asis"}
```

By Rank and Billet Type
-----------------------------------
```{r by-billet-and-rate, echo=echo_chunks, message=message_chunks, results="asis"}
```

Ordinal Models
===================================

-----------------------------------
```{r 3-predictor-ordinal, echo=echo_chunks, message=message_chunks, results="asis"}
```

Models to Publish
===================================

3-predictor (and final) model
-----------------------------------
```{r 3-predictor, echo=echo_chunks, message=message_chunks, results="asis"}
```

3-predictor model weight sampling weights
-----------------------------------
```{r 3-predictor-with-weights, echo=echo_chunks, message=message_chunks, results="asis"}
```


Billet Intercepts
-----------------------------------
```{r billet-intercept, echo=echo_chunks, message=message_chunks, results="asis"}
```

Specialty Intercepts
-----------------------------------
```{r specialty-intercept, echo=echo_chunks, message=message_chunks, results="asis"}
```


Nonsignificant Additions
-----------------------------------
```{r nonsignificant-additions, echo=echo_chunks, message=message_chunks}
```


Session Information
============================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
} 
```
</details>

```{r session-duration, echo=FALSE}
report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.
